Speed and strength of an epidemic intervention

### 2020-10-19 speedstrength.tex
meeting with Daniel

Since we are interested in invasion and control, we will generally neglect changes in $K(\tau, t)$ through time.
Thus, we will assume $K(\tau, t) \equiv K(\tau)$.
Importantly, this means we are neglecting changes in susceptible proportion through time: that is, assuming that $S(t) \approx S(0)$.
Under this assumption, the renewal equation is equivalent to the Von Foerster equations (see e.g. \cite{fraser2004factors}).
Note that this focus does not mean we are only interested in the initial period of exponential growth: the ability of a disease to increase under conditions characteristic of a naive population is commonly used as a criterion for whether it can be eliminated under general conditions \citep{anderson1985vaccination,fraser2004factors}.
\swp{I feel like there's too much ``something, ...'' phrasing. How about the following?} 
Since we are interested in invasion and control, we will generally neglect changes in $K(\tau, t)$ through time and assume $K(\tau, t) \equiv K(\tau)$.
Importantly, this means we are neglecting changes in susceptible proportion through time: $S(t) \approx S(0)$.
Under this assumption, the renewal equation is equivalent to the Von Foerster equations (see e.g. \cite{fraser2004factors}).
However, this focus does not mean we are only interested in the initial period of exponential growth: the ability of a disease to spread under conditions characteristic of a naive population is commonly used as a criterion for whether it can be eliminated under general conditions \citep{anderson1985vaccination,fraser2004factors}.
\swp{``conditions characteristic of a naive population'' doesn't really make sense...}

@@

We define the strength of the intervention $L$ to be $\theta = \RR/\Rhat$. 
It is then straightforward to show that $\theta$ is the harmonic mean of $L(\tau)$ weighted by the intrinsic generation-interval distribution:
\begin{equation}
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)}.
	\eqlab{strengthMean}
\end{equation}
As in the constant-$L$ case above, we have that the disease cannot spread when $\theta \geq \RR$. 
In other words, $\theta$ generalizes the well-known idea that \RR\ is a metric for how hard a disease is to eliminate: we can measure the ``strength'' of a control measure, this must exceed the strength of the disease (\RR) to achieve elimination.
\swp{The last two/three sentences feel repetitive.}

>>>>

Since we are interested in invasion and control, we will generally neglect changes in $K(\tau, t)$ through time and assume $K(\tau, t) \equiv K(\tau)$.
Importantly, this means we are neglecting changes in susceptible proportion through time: $S(t) \approx S(0)$.
Under this assumption, the renewal equation is equivalent to the Von Foerster equations (see e.g. \cite{fraser2004factors}).
However, this focus does not mean we are only interested in the initial period of exponential growth: the ability of a disease to spread under conditions characteristic of a naive population is commonly used as a criterion for whether it can be eliminated under general conditions \citep{anderson1985vaccination,fraser2004factors}.

@@

We define the strength of the intervention $L$ to be $\theta = \RR/\Rhat$. 
It is then straightforward to show that $\theta$ is the harmonic mean of $L(\tau)$ weighted by the intrinsic generation-interval distribution:
\begin{equation}
	\theta = 1/\langle 1/L(\tau) \rangle_{g(\tau)}.
	\eqlab{strengthMean}
\end{equation}
As in the constant-$L$ case above, we have that the disease cannot spread when $\theta \geq \RR$. 
In other words, $\theta$ generalizes the well-known idea that \RR\ is a metric for how hard a disease is to eliminate: we can measure the ``strength'' of a control measure, this must exceed the strength of the disease (\RR) to achieve elimination.
